Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-01-11 hscc2017/paper.tex
nudge

Proposition~\ref{prop:eq_int_stab} provides the necessary conditions for the
controller to stabilize the closed-loop system, considering plant
parametric uncertainties (i.e., $\Delta_p \vec{G}$), quantization noises
($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Note
that the model for plant uncertainty due to quantization noise (i.e.,
$\Delta_q \vec{G}$) may be disregarded if the conditions on
Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization
noise is bounded.  The quantization noise boundedness comes from
Assumption~\ref{whitenoise}.

@@

Next, the following Jury matrix
$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right), 
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N - 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if the following four conditions hold:
%\begin{itemize}
%\item 
$R_1: S(1) > 0$;
%\item 
$R_2: (−1)^N S(−1) > 0$;
%\item 
$R_3: |a_0| < a_N$;
%\item 
$R_4: m_{11} > 0 \wedge m_{31}>0 \wedge m_{51}>0 \wedge \cdots \wedge m_{(2N{-}3)(1)}>0$.
%\end{itemize}
%
The stability property is then encoded by creating a
constraint of the form:
$
\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}

@@

The {\sc synthesize} phase uses BMC to 
compute a solution $C(z)$. % An important remark is that this 
% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
% domain.
There are two approaches for the {\sc verify} phase.
% based on the described model.  
The first approach uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i\ ,\
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$ 
and rounds operations outwards during calculations.  This effectively allows
us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
plus the effects of numeric calculations in the engine.  Synthesized
controllers using this verifier will always be stable for all plants in the
family.
% and only generate counterexamples when the precision of the
%engine is insufficient (\emph{ie} no stable plant could be found). 
Our preliminary experiments showed that a synthesis approach
using this verification engine has poor performance and we
%Given the high computational cost of this
%approach, 
therefore designed a second approach, which we describe below.
Our experimental results described in Section~\ref{sec:experiments}
%try both approaches and provide the time for the fastest. 
show that the speedup yielded by the second approach 
is in most cases of at least two orders of magnitude.

>>>>

Proposition~\ref{prop:eq_int_stab} provides the necessary conditions for the
controller to stabilize the closed-loop system, considering plant
parametric uncertainties (i.e., $\Delta_p \vec{G}$), quantization noises
($\nu_{1}$ and $\nu_{2}$) and FWL effects in the control software.  Note
that the model for plant uncertainty due to quantization noise (i.e.,
$\Delta_q \vec{G}$) may be disregarded if the conditions on
Proposition~\ref{prop:eq_int_stab} are satisfied and if the quantization
noise is bounded.  The bound on the quantization noise is given by
Assumption~\ref{whitenoise}.

@@

Next, the following Jury matrix
$M = [m_{ij}]_{(2N-2)\times N}$ is built from $S(z)$ coefficients:
%
$$
M=\left( 
\begin{array}{c}
V^{(0)}\\
V^{(1)}\\
\vdots\\
V^{(N-2)}
\end{array}
\right), 
$$
%
where $V^{(k)} = [v^{(k)}_{ij} ]_{2\times N}$ such that:
%
$$
v_{ij}^{(0)}=\left\{
\begin{array}{ll}
a_{j-1}, & \texttt{if}~i=1\\
v_{(1)(N-j+1)}^{0},&\texttt{if}~i=2
\end{array}
\right.
$$
%
$$
v_{ij}^{(k)}=\left\{
\begin{array}{ll}
0,&\texttt{if}~j>n-k\\
v_{1j}^{(k-1)}-v_{2j}^{(k-1)} . \frac{v_{11}^{(k-1)}}{v_{21}^{(k-1)}}, & \texttt{if}~j\leq n-k ~\texttt{and}~i=1\\
v_{(1)(N-j+1)}^{k},& \texttt{if}~j\leq n-k ~\texttt{and}~i=2\\
\end{array}
\right.
$$
%
where $k \in \mathbb{Z}$, such that $0 < k < N - 2$. 
$S(z)$ is the
characteristic polynomial of a stable system if and only if the following four conditions hold:
%\begin{itemize}
%\item 
$R_1: S(1) > 0$;
%\item 
$R_2: (−1)^N S(−1) > 0$;
%\item 
$R_3: |a_0| < a_N$;
%\item 
$R_4: m_{11} > 0 \wedge\allowbreak
      m_{31}>0 \wedge\allowbreak
      m_{51}>0 \wedge \ldots \wedge\allowbreak
      m_{(2N{-}3)(1)}>0$.
%\end{itemize}
%
The stability property is then encoded by a constraint of the form:
$
\phi_\mathit{stability} \equiv (R_1 \wedge R_2 \wedge R_3 \wedge R_4).
$
%\cdsay{figure out what is existentially quantified for the final $\sigma$.} 
%% \red{[Yes, intuitively all clear, however for the sake of clarity I would like to see the explicit mapping between the above formula and the previously used specification 
%% $\sigma(x, P)$, with clear elucidation of the relationship between the domain of $z$ and that of $x$.]}

@@

The {\sc synthesize} phase uses BMC to 
compute a solution $C(z)$. % An important remark is that this 
% controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
% domain.
There are two approaches for the {\sc verify} phase.
% based on the described model.  
The first approach uses interval arithmetic \cite{moore1966interval}
to represent the coefficients
$[{c}_i-\Delta_p{c}_i-\Delta_b{c}_i,\,\allowbreak
{c}_i+\Delta_p{c}_i-\Delta_b{c}_i+(2^{-F_p})]$ 
and rounds operations outwards during calculations.  This effectively allows
us to simultaneously evaluate the whole collection of plants $\mathfrak{G}$
plus the effects of numeric calculations in the engine.  Synthesized
controllers using this verifier will always be stable for all plants in the
family.
% and only generate counterexamples when the precision of the
%engine is insufficient (\emph{ie} no stable plant could be found). 
Our preliminary experiments showed that a synthesis approach
using this verification engine has poor performance and we
%Given the high computational cost of this
%approach, 
therefore designed a second approach, which we describe below.
Our experimental results described in Section~\ref{sec:experiments}
%try both approaches and provide the time for the fastest. 
show that the speedup yielded by the second approach 
is in most cases of at least two orders of magnitude.
